MYC overrides HIF-1α to regulate proliferating primary cell metabolism in hypoxia

### 2023-02-16 manuscript/manuscript.qmd
learn to add pagebreaks

format:
  docx:
    reference-doc:  template.docx
    page-width: 7.5
    output-file: copeland_2023_flux_manuscript.docx

filters:
    - scholarly-metadata.lua
    - author-info-blocks.lua

---

@@

>>>>

format:
  docx:
    reference-doc:  template.docx
    page-width: 7.5

output-file: copeland_2023_flux_manuscript.docx

filters:
    - scholarly-metadata.lua
    - author-info-blocks.lua
---

@@

{{< pagebreak >}}
